Democracy, Public Support, and Measurement Uncertainty

### 2021-06-01 paper/dcpo_demsupport.Rmd
fixed the issue of dcpomean

claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)
load(here("data", "claassen_m5_theta.rda"))
load(here("data", "dem_mood_apsr.RData"))
load(here("data", "dcpo_input.rda"))
# load(here::here("data", "dcpo_theta.rda"))
# load(here::here("data", "dcpo_sigma.rda"))
# load(here("data", "dcpo_ajps_rubin.rda"))

@@

# the readRDS produced "unknown format" error, very weild
# saveRDS(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
# df_dcpoMean <- readRDS(here::here("output", "estimates_dcpoMean.RDS"))

df_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name"),
         regime = Vdem_regime > 1) %>% 
  filter(year >= firstyear) # using trimmed data as Claassen

@@

@@

```{r dcpoUncertaintyAJPS}
df_dcpo <- dcpo_ajps_rubin %>% map(~ .)

>>>>

claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)
load(here("data", "claassen_m5_theta.rda"))
load(here("data", "dem_mood_apsr.RData"))
load(here("data", "dcpo_input.rda"))
load(here("data", "dcpo_theta.rda"))
load(here("data", "dcpo_sigma.rda"))
load(here("data", "dcpo_ajps_rubin.rda"))

@@

# the readRDS produced "unknown format" error, very weild

df_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(
         country = countrycode::countrycode(country, "country.name", "country.name"),
         regime = Vdem_regime > 1) %>% 
  filter(year >= first_year) # using trimmed data as Claassen

@@

#There's a problem to run this part---------------------

@@

```{r dcpoUncertaintyAJPS}
load(here("data", "dcpo_ajps_rubin.rda"))

df_dcpo <- dcpo_ajps_rubin %>% map(~ .)
